Deciding to Disclose

### 2015-11-10 disclosure_game.tex
Cleaning up
Moving table caps
Finally fixed the tables
Build errors
Correct NICE acronym
Rewrite game theory -> decision theory bit
Rearrange payoff tables
To save some space
Additional figs
Tweaks
acronyms to own file

\usepackage{comment}
 \usepackage{natbib}
 \setcitestyle{numbers,square}
% \usepackage{hyperref}
 \usepackage{graphicx}
 \usepackage[subrefformat=parens,labelformat=simple,caption=false,labelfont={bf}]{subfig}
 \usepackage[nolist,smaller]{acronym}
 \usepackage{sidecap}
% \usepackage{nomencl}
\makeindex

\begin{document}
\begin{acronym}[ALSPAC]
  \acro{FAS}{Foetal Alcohol Syndrome}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{PT}{Prospect Theory}
  \acro{NICE}{National Institute for Health and Care Excellence}
  \acro{IAPT}{Improving Access to Psychological Therapies}
  \acro{CMACE}{Centre for Maternal and Child Enquiries}
  \acroindefinite{CMACE}{the}{the}
  \acro{AUDIT}{Alcohol Use Disorders Identification Test}
  \acro{T-ACE}{Tolerance, Annoyance, Cut down, Eye-opener}
  \acro{RCOG}{Royal College of Obstetricians and Gynecologists}
  \acroindefinite{RCOG}{the}{the}
  \acro{AML}{acute myeloid leukemia}
  \acro{ADHD}{Attention Defecit Hyperactivity Disorder}
  \acro{PND}{Postnatal Depression}
  \acro{RCT}{randomised control trial}
  \acro{WHO}{the World Health Organisation}
  \acro{ESS}{Evolutionarily Stable Strategy}
  \acrodefplural{ESS}[ESS]{Evolutionarily Stable Strategies}
  \acro{MCMC}{Markov chain monte carlo methods}
  \acro{DU}{Discounted Utility}
  \acro{AIC}{Akaike information criterion}
  \acro{ANOVA}{analysis of variance}
  \acro{ALSPAC}{the Avon Longitudinal Study of Parents and Children}
  \acro{GEM}{Gaussian Emulation Machine}
  \acrodefplural{GEM}{Gaussian Emulation Machines}
  \acro{GEM-SA}{Gaussian Emulation Machine for Sensitivity Analysis}
  \acro{JIT}{Just-in-time}
  \acro{ABM}{Agent Based Modelling}
  \acro{ABMs}{Agent Based Models}
  \acro{CPT}{Cumulative Prospect Theory}
  \acro{FFH}{Fast and Frugal Heuristic}
  \acro{OFC}{orbito-frontal cortex}
  \acro{BACCO}{Bayesian Analysis of Computer Code Outputs}
  \acro{IQR}{interquartile range}
\end{acronym}

@@

%Assuming this is for JASSS.. Need to make background shorter.
%Aim for ~ 7-8,000 words overall.

@@

%\input{Background}

\input{Model}
\input{agent_models}

@@

\bibliography{library,library_addendum}
\bibliographystyle{spbasic}
\input{SensitivityAnalysis}
\input{model_description}
\input{simulation_schedule}
\input{agent_examples}
\end{document}

>>>>

\usepackage{comment}
 \usepackage{natbib}
 \setcitestyle{numbers,square}
% \usepackage{hyperref}
 \usepackage[subrefformat=parens,labelformat=simple,caption=false,labelfont={bf}]{subfig}
%\usepackage{floatrow}
 \usepackage[nolist,smaller]{acronym}
% \usepackage{nomencl}
\allowdisplaybreaks
\makeindex

\begin{document}
\begin{acronym}[ALSPAC]
  \input{acronyms}
\end{acronym}

@@

@@

%\input{Background}
%\input{motivation}
\input{Model}
\input{agent_models}

@@

\bibliography{library,library_addendum}
\bibliographystyle{spbasic}
\input{model_description}
\input{simulation_schedule}
\input{agent_examples}
\input{add_figures}
\input{SensitivityAnalysis}
\end{document}
